---
title: 'Project 3: Data Exploration'
author: "Alice Ding"
date: "2023-03-14"
output: pdf_document
---

```{r connect to Azure SQL Server}
library(tidyverse)
library(odbc)
library(DBI)
library(keyring)

if (!("Overview8909" %in% as_vector(key_list()[2]))) {
  key_set("Project3SQL","Overview8909")
}
```

#### Configuring Database Tables

As this is a fresh Azure SQL server instance, we want to create the tables that will hold the information of our dataset. We initialize the tables with our queries.

```{r Configuring Database Tables}
my_connection <- dbConnect(drv = odbc::odbc(),
                           Driver = "ODBC Driver 17 for SQL Server",
                           server = "tcp:data607project3server.database.windows.net,1433",
                           database = "Data 607 Project 3 Database",
                           uid = "Overview8909",
                           pwd = key_get("Project3SQL","Overview8909"),
                           encoding = "latin1"
                           )